Which ITG Stepcharts are Turniest?

### 2016-03-14 itg/paper.tex
fix some stuff

{\bf Minimum turniness.}
Each of the 5 categories shares the same data point at $\mathcal{T}=0$: there are 7 possible streams that never turn at all. These are the 7 ``tower'' patterns $LULU$, $LRLR$, $LDLD$, $URUR$, $DRDR$, $UDUD$, and $DUDU$. We already showed the first of these in Figure~\ref{fig:stream}, left. For further treatment of minimally turny charts, we refer the reader to \cite{deltamax}.

@@

\begin{figure*}[t]
	\begin{center}
	\begin{tabular}{cccc}
		\hspace{-1em}
		\begin{tabular}{c}
		\includegraphics[width=0.18\textwidth]{do-me.png} \\
		\small
		\begin{tabular}{l}
			(a) {\em DO ME}, $\mathcal{T}=1.63$. \\
			Proportion of non-spinny \\
			section enlarged to show \\
			detail. \\
		\end{tabular}
		\end{tabular}
		&
		\hspace{-1em}
		\begin{tabular}{c}
		\includegraphics[width=0.18\textwidth]{mr-saxobeat.png} \\
		\small
		\begin{tabular}{l}
			(b) {\em Mr. Saxobeat}, $\mathcal{T}=1.04$. \\
		Look at all those candles! \\
		No wonder it was so hard \\
		for the author to pass.\\
		\end{tabular}
		\end{tabular}
		&
		\hspace{-2em}
		\begin{tabular}{c}
		\includegraphics[width=0.185\textwidth]{flames.png} \\
		\small
		\begin{tabular}{l}
			(c) {\em Flames of the Sky}, $\mathcal{T}=1.04$. \\
			False-positive $\mathcal{T}$ from foot-\\
		switches. Actually faces $R$/$UR$/\\
		$U$/$UL$/$L$ the whole time.
		\end{tabular}
		\end{tabular}
		&
		\hspace{-2em}
		\begin{tabular}{c}
		\includegraphics[width=0.18\textwidth]{sick-dubstep-track.png} \\
		\small
		\begin{tabular}{l}
			(d) {\em Sick Dubstep Track}, $\mathcal{T}=$ \\
			$0.26$. 
		The least turny non- \\trivial
		non-beginner chart.\\
		\\
		\end{tabular}
		\end{tabular}
	\end{tabular}
	\end{center}
	\caption{Real-world ITG charts of varying degrees of turniness.}
	\label{fig:example}
\end{figure*}

>>>>

{\bf Minimum turniness.}
Each of the 5 categories shares the same data point at $\mathcal{T}=0$: there are 7 possible streams that never turn at all. These are the 7 ``tower'' patterns $LRLR$, $LULU$, $LDLD$, $URUR$, $DRDR$, $UDUD$, and $DUDU$. We already showed the first of these in Figure~\ref{fig:stream}, left. For further treatment of minimally turny charts, we refer the reader to \cite{deltamax}.

@@

\begin{figure*}[t]
	\begin{center}
	\begin{tabular}{cccc}
		\hspace{-1em}
		\begin{tabular}{c}
		\includegraphics[width=0.169\textwidth]{do-me.png} \\
		\small
		\begin{tabular}{l}
			(a) {\em DO ME}, $\mathcal{T}=1.63$. \\
			Proportion of non-spinny \\
			section enlarged to show \\
			detail. \\
		\end{tabular}
		\end{tabular}
		&
		\hspace{-1em}
		\begin{tabular}{c}
		\includegraphics[width=0.169\textwidth]{mr-saxobeat.png} \\
		\small
		\begin{tabular}{l}
			(b) {\em Mr. Saxobeat}, $\mathcal{T}=1.04$. \\
		Look at all those candles! \\
		No wonder it was so hard \\
		for us to pass this one.\\
		\end{tabular}
		\end{tabular}
		&
		\hspace{-2em}
		\begin{tabular}{c}
		\includegraphics[width=0.169\textwidth]{flames.png} \\
		\small
		\begin{tabular}{l}
			(c) {\em Flames of the Sky}, $\mathcal{T}=1.04$. \\
			False-positive $\mathcal{T}$ from foot-\\
		switches. Actually faces $R$/$UR$/\\
		$U$/$UL$/$L$ the whole time.
		\end{tabular}
		\end{tabular}
		&
		\hspace{-2em}
		\begin{tabular}{c}
		\includegraphics[width=0.169\textwidth]{sick-dubstep-track.png} \\
		\small
		\begin{tabular}{l}
			(d) {\em Sick Dubstep Track}, $\mathcal{T}=$ \\
			$0.26$. 
		The least turny non- \\trivial
		non-beginner chart.\\
		\\
		\end{tabular}
		\end{tabular}
	\end{tabular}
	\end{center}
	\caption{Real-world ITG charts of varying degrees of turniness.}
	\label{fig:example}
\end{figure*}
